Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex
paper: overfitting

\subsubsection{Training Progress Diagram}

TODO: Describe training progress diagrams.

>>>>

\subsubsection{Training Progress Diagram}
As we all know, there will be overfitting if we train too "hard" on training set. And if overfitting happens, the test accuracy, in our experiments is out-of-domain accuracy, will drop. Figure \ref{Adagrad_fig} shows this drop on both total accuracy and unknown word accuracy.
